### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor changes to CAF report

The series of tests described within this report were conducted at the Delaware County ESTC in Sharon Hill, PA. A burn building and two purpose-built concrete structures are located on the grounds of the ESTC. The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments. Figure~\ref{fig:Door_Status_Legend} provides the key for determining the status of open or closed doors in the facility schematics.

@@

The burn building, or live fire training structure, contained a two-story section and a three-story section. The building was supported with reinforced concrete beams and columns. The floors and ceilings were also concrete, and the interior walls were constructed of cement block. The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile. The floors of the burn rooms were protected with fire brick. Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft). Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.

@@

The 88 gas cooling experiments were completed as part of nine separate burn sequences in the burn building. For detailed discussion on each of the individual events, refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}. While Mitchell examined each individual experiment in detail, the results were mixed. In the different gas cooling scenarios, CAF showed slightly better or slightly worse than plain water. Hence, the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.

@@

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used. The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3). This is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 also exhibits some amount of suppression agent impact.  Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.  As a result, it remained dry and seems to provide the best representation of the gas cooling.   
`'
\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent}
	\label{fig:gas_cooling_sub1}
\end{figure}

@@

To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the fire room. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3). Ideally, the thermocouple is providing an estimate of the temperature of the gas that surrounded it. However, the thermocouple is actually measuring its own temperature. So, if a droplet of water or some CAF clings to a thermocouple, the temperature provided by that thermocouple will be different than the surrounding gas temperature.

>>>>

The series of tests described within this report were conducted at the Delaware County ESTC in Sharon Hill, PA. A burn building and two purpose-built concrete structures are located on the grounds of the ESTC. The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments. Figure~\ref{fig:Door_Status_Legend} provides the key used to identify doors and windows in the facility schematics.

@@

The burn building, or live fire training structure, contained a two-story section and a three-story section. The building was supported with reinforced concrete beams and columns. The floors and ceilings were also concrete, and the interior walls were constructed of cement block. The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile. The floors of the burn rooms were protected with fire brick. Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft). Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor. A fully dimensioned plan view of the floor is presented in Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout_Detailed} in Appendix~\ref{app:floor_plans}.

@@

The 88 gas cooling experiments were completed as part of nine separate burn sequences in the burn building. For detailed discussion on each of the individual events, refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}. While Mitchell examined each individual experiment in detail, the results were mixed. In the different gas cooling scenarios, CAF performed slightly better or slightly worse than plain water. Hence, the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.

@@

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used. The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3). This is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 also exhibits some amount of suppression agent impact.  Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.  As a result, it remained dry and seems to provide the best representation of the gas cooling.

\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent}
	\label{fig:gas_cooling_sub1}
\end{figure}

@@

To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the gas cooling room. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3). Ideally, the thermocouple is providing an estimate of the temperature of the gas that surrounded it. However, the thermocouple is actually measuring its own temperature. So, if a droplet of water or some CAF clings to a thermocouple, the temperature provided by that thermocouple will be different than the surrounding gas temperature.
